Sequential Decision-Making under Uncertainty with Big Data

### 2023-04-13 paper/main.tex
commit for pual

% Parameters
\newcommand{\transitionParams}{\ensuremath{\bm\phi}}
\newcommand{\valueFnParams}{\ensuremath{\psi}}
\newcommand{\policyParams}{\ensuremath{\theta}}

@@

@@

In this section, we recap how to fit a GP posterior to a trained deep neural network (DNN).
We start by obtaining a posterior over the weights of a trained neural network via the Laplace approximation.
We then show how we can obtain a function-space posterior, (i.e. a GP posterior)
by linearising the neural network around the weights Maximum a Posteriori (MAP) estimate.
% We then show that by linearising the neural network we can obtain a function-space posterior, i.e. a GP posterior.

% We paraterise our single-step dynamic model $\transitionFnWithParams : \inputDomain \rightarrow \outputDomain$
% as an $L\text{-layer}$ NN with weights $\transitionParams$.
Given a data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
the goal of (supervised) deep learning, is to train the weights $\transitionParams \in \R^{P}$ of an $L\text{-layer}$ NN
$f : \inputDomain \rightarrow \outputDomain$ to minimize the (regularized) empirical risk,
\begin{align}
  \transitionParams^{*} = \arg \min_{\transitionParams \in \R^{D}} \mathcal{L}(\dataset;\transitionParams) = \arg \min_{\transitionParams \in \R^{D}} \left(
  R(\transitionParams) + \sum_{n=0}^{N-1} l(f(\mathbf{x}_{n} ; \transitionParams), \mathbf{y}_{n}) \right).
\end{align}
In practice, it is common to use the mean squared error (MSE) loss
$l(f(\mathbf{x}_{n} ; \transitionParams),\mathbf{y}_{n}) = \|f(\mathbf{x}_{n} ; \transitionParams) - \mathbf{y}_{n} \|^{2}_{2}$
and to use the weight decay regularizer $R(\transitionParams)=\frac{1}{2}\gamma^{-2}\|\transitionParams\|^{2}_{2}$.
However, the practioner is free to choose any loss and regularizer. \todo{I think?}

\textbf{Laplace approximation}
The Laplace approximation \todo{add citation of original paper} constructs a Gaussian approximation of the weight-space posterior $p(\transitionParams \mid \dataset)$
by using a second-order Taylor expansion of $\mathcal{L}$ around $\transitionParams^{*}$.
The posterior approximation is given by,
\begin{align} \label{eq-laplace-approx-weight-space}
  p(\transitionParams \mid \dataset) \approx \mathcal{N} \left( \transitionParams \mid \transitionParams^{*} , \bm\Sigma_{\transitionParams^{*}} \right)
  \quad \text{with} \quad \bm\Sigma_{\transitionParams} =
 - \nabla_{\transitionParams \transitionParams}^{2} \mathcal{L} ( \dataset ; \transitionParams)|_{\transitionParams=\transitionParams^{*}}
\end{align}
That is, it sets the posterior precision to the Hessian of the loss at the optimal parameters $\transitionParams^{*}$.
It is worth noting that computing the Hessian of the loss can be computationally intractable for large networks.
The prior terms are usually trivial, so we will focus on the likelihood here.
The Jacobian and Hessian of the log likelihood can be expressed per data point,
\begin{align} \label{eq-jac}
  \nabla_{\transitionParams} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \transitionParams)) &= \mathbf{J}(\mathbf{x})^{T} \mathbf{r}(\mathbf{y} ; \mathbf{f}) \\
  \nabla^{2}_{\transitionParams\transitionParams} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \transitionParams)) &= \mathbf{H}(\mathbf{x})^{T}
  \mathbf{r}(\mathbf{y};\mathbf{f}) - \mathbf{J}(\mathbf{x})^{T} \bm\Lambda(\mathbf{y};\mathbf{f}) \mathbf{J}(\mathbf{x}),
\label{eq-hess}
\end{align}
through the Jacobian $\mathbf{J} \in \R^{C \times P}$ and Hessian $\mathbf{H} \in \R^{C \times P \times P}$ of the feature extractor $\mathbf{f}(\mathbf{x}; \bm\transitionParams)$,
\begin{align} \label{eq-jac}
[\mathbf{J}(\cdot)]_{ci} = \odv{f_{c}(\cdot ; \transitionParams)}{\transitionParams_{i}}_{\transitionParams=\transitionParams^{*}} \qquad
[\mathbf{H}(\cdot)]_{cij} = \odv{f_{c}(\cdot ; \transitionParams)}{\transitionParams_{i}\transitionParams_{j}}_{\transitionParams=\transitionParams^{*}}
\end{align}
where
$\mathbf{r}(\mathbf{y}; \mathbf{f}) = \nabla_{\mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be interpreted as a residual and
$\bm\Lambda(\mathbf{y} ; \mathbf{f}) = \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$
as per-input noise.
Many approximations exist and can be used alongsied our method.
We refer the reader to \cite{daxbergerLaplace2021} for more details.
See \cref{sec-laplace-approximation} for further details on the Laplace approximation.

% \begin{align}
% \Sigma_{\transitionParams_{i}}^{-1} = - \nabla_{\transitionParams \transitionParams}^{2} \log p(\transitionParams \mid \dataset_{0:i})|_{\transitionParams=\transitionParams^{*}_{i}}
%   + \frac{1}{\sigma^{2}_{0}} \mathbf{I}
% \end{align}

\textbf{Weight space to function space}
% We can represent the log joint density in the function space,
% \begin{align} \label{eq-laplace-approx-function-space}
%   \sum_{n=1}^{N} \log p \left(y_{n} \mid f(\mathbf{x}_{n} ; \transitionParams_{0:i}) \right) + \log p(f(\mathbf{X}; \transitionParams_{0:i}))
% \end{align}
We can represent the weight space posterior from \cref{eq-laplace-approx-weight-space}, in
function space, by linearising the BNN and interpretting it as a GP.
The GP prior is then given by,
\begin{align} \label{eq-laplace-approx-function-space}
  % \transitionFn_{\transitionParams_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \qquad
  f(\cdot ;\transitionParams) \sim \mathcal{N} \left( \mu(\cdot), k(\cdot, \cdot') \right) \qquad
  % \mu_{\transitionParams_{i}^{*}}(\cdot)
  \mu(\cdot)
  = f(\cdot ;\transitionParams^{*}) \qquad
  % K_{\transitionParams_{i}^{*}}(\cdot, \cdot')
  k(\cdot, \cdot')
  = \gamma^{2} \mathbf{J}(\cdot) \mathbf{J}(\cdot')^{T},
\end{align}
where the kernel is the neural tangent kernel (NTK) \parencite{immerImprovingPredictionsBayesian2021}.
\todo{what mean function shoudl this use???}
\todo{NTK times some factor??}
% with Jacobian given by $\mathbf{J}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}$.
% The kernel in \cref{eq-laplace-approx-function-space} is the neural tangent kernel (NTK)
% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\transitionParams^{*}}(\mathbf{x}) J_{\transitionParams^{*}}(\mathbf{x}')^{T}$
% \parencite{immerImprovingPredictionsBayesian2021}
% to formulate the GP posterior $p(f(\mathbf{X} ;\transitionParams_{0:i}) \mid \dataset_{0:i})$.
It is worth noting that the NTK linearises the network around the optimised parameters $\transitionParams_{i}^{*}$,
so the function space prior (and thus posterior) is only a locally linear approximation.
In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
Given our GP prior, we can use the properties of multivariate normals to obtain our GP posterior by conditioning on the data.
Our GP posterior is given by,
\todo{add mean func to GP posterior if we're using one}
\begin{align} \label{eq-gp-predictive-posterior}
  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
  \left( f(\mathbf{x}_{*}) \mid \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} \mathbf{m}^{*},
  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} + \bm\Lambda(\mathbf{y} ; \mathbf{f})^{-1} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
\end{align}

\section{Dual SVGP} \label{sec:method}
The GP predictive posterior in \cref{eq-gp-predictive-posterior} is computationally expensive
as it requires inverting $N\times N$ matrix.
Sparse approximations using pseudo points ...
\begin{align} \label{eq-svgp-predictive-posterior}
  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
  \left( f(\mathbf{x}_{*}) \mid \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} \mathbf{m}^{*},
  k_{**} - \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} \mathbf{k}_{*\mathbf{x}}^{T} \right) \\
  % &\approx \mathcal{N}
  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} \mathbf{A}^{T} + \mathbf{A} \mathbf{V}^{*} \mathbf{A}^{T} \right) \\
&\approx \mathcal{N} \left( f(\mathbf{x}_{*}) \mid \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{m}^{*},
  k_{**} - \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
  % \mathbf{k}_{*\inducingInput} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\inducingInput}^{T}
  + \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}}  \mathbf{V}^{*}  \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
  \right)
\coloneqq q_{\inducingVariable}(f(\mathbf{x}_{*}))
\end{align}
% where $\mathbf{A} = \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}}$

@@

\section{Experiments}
Environments
\begin{itemize}
  \item Compare updated posterior with non updated posterior
  \item Need to show update is fast enough for practical use?
  \begin{itemize}
    \item How frequently can we do the posterior update? Every time step or every $K$ steps?
    \item Update depends on number of inducing points?
    \item What experiments can we show for this? Wall clock time vs planning horizon with different numbers of inducing points?
  \end{itemize}
  \item Is linearising NN mean and using fast updates during episode better than keeping non-linearised mean and not updating?
  \item How does number of inducing points affect performance?
  \begin{itemize}
    \item More inducing points means better approximation but larger computational complexity.
  \end{itemize}
  \item How good is the assumption that we can linearise BNN to get NTK?
  \begin{itemize}
    \item Does model's performance get worse during an episode because linearisation becomes more wrong?
    \item SVGP does't have this issue so compare to SVGP in cartpole?
  \end{itemize}
  \item What length planning horizon to use?
  \begin{itemize}
    \item Too small (e.g. $\Horizon=0$) would mean no exploration?
    \item Can $\Horizon$ be too large?
  \end{itemize}
  \begin{itemize}
  \item Compare for different strategies of making decisions under dynamic model's uncertainty:
    \begin{itemize}
      \item \textbf{Greedy exploitation} \(\pi_{\text{greedy}}\)
      \item \textbf{Hallucinated-UCRL} \(\pi_{\text{HUCRL}}\)
      \item \textbf{Thompson sampling} \(\pi_{\text{TS}}\)
    \end{itemize}
  \end{itemize}
  \item Compare impact of stationary vs non-stationary priors
  \begin{itemize}
    \item First do this with GP
    \item Then try to do with Laplace BNN
  \end{itemize}
  \item Compare impact of function vs weight space
\end{itemize}

@@

>>>>

% Parameters
% \newcommand{\transitionParams}{\ensuremath{\bm\phi}}
\newcommand{\transitionParams}{\ensuremath{\mathbf{w}}}
\newcommand{\valueFnParams}{\ensuremath{\psi}}
\newcommand{\policyParams}{\ensuremath{\theta}}

@@

% \section{Background} \label{sec:background}
% In this section, we recap how to fit a GP posterior to a trained deep neural network (DNN).
% We start by obtaining a posterior over the weights of a trained neural network via the Laplace approximation.
% We then show how we can obtain a function-space posterior, (i.e. a GP posterior)
% by linearising the neural network around the weights Maximum a Posteriori (MAP) estimate.
% % We then show that by linearising the neural network we can obtain a function-space posterior, i.e. a GP posterior.

@@

In this section, we recap how can obtain a GP posterior from a trained deep neural network (DNN).
% We start by obtaining a posterior over the weights of a trained neural network via the Laplace approximation.
% We then show how we can obtain a function-space posterior, (i.e. a GP posterior)
% by linearising the neural network around the weights Maximum a Posteriori (MAP) estimate.
% We then show that by linearising the neural network we can obtain a function-space posterior, i.e. a GP posterior.
% We paraterise our single-step dynamic model $\transitionFnWithParams : \inputDomain \rightarrow \outputDomain$
% as an $L\text{-layer}$ NN with weights $\transitionParams$.
\textbf{Gaussian processes}
A Gaussian process (GP) is a distribution over real-valued functions $f(\cdot): \mathcal{X} \rightarrow \R$ defined over $\mathcal{X}$.
Formally, a GP is defined as,
\begin{align}
\label{eq-gp-prior}
  f(\cdot) \sim \mathcal{N}\left( \mu(\cdot), k(\cdot,\cdot') \right) \quad
  \mu(\cdot): \mathcal{X} \rightarrow \R \quad
  k(\cdot,\cdot'): \mathcal{X} \times \mathcal{X} \rightarrow \R
\end{align}
where $\mu(\cdot)$ denotes a mean function and $k(\cdot,\cdot')$ a positive definite covariance function, also known as a kernel.
Given a data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
we can obtain the GP posterior via multivariate normal conditioning,
\begin{align}
\label{eq-gp-predictive-posterior}
  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} (\mathbf{y} - \bm\mu_{\mathbf{X}})),
  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
\end{align}
% Our GP posterior is then given by,
\todo{add mean func to GP posterior if we're using one}
\begin{align}
\label{eq-gp-predictive-posterior}
  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} \mu_{\mathbf{x}},
  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} + \bm\Lambda(\mathbf{y} ; \mathbf{f})^{-1} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
\end{align}
where $\bm\Lambda(\mathbf{y} ; \mathbf{f}) = \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be viewed as per-input noise. \todo{I'm unsure about this per input noise bit. Check with paul.}
\todo{what about regression/classification likelhoods}
This GP predictive posterior is computationally expensive as it requires inverting an $N\times N$ matrix.

\textbf{Sparse Gaussian processes}
% The GP predictive posterior in \cref{eq-gp-predictive-posterior} is computationally expensive as it requires inverting an $N\times N$ matrix.
A practical and computationally appealing alternative is to augment the joint probability space with pseudo inputs $\mathbf{Z} \in \R^{M \times D}$
and corresponding outputs
$\mathbf{u} = f(\mathbf{Z}; \transitionParams) \in \R^{M \times C}$, known as inducing variables, where $M \ll N$.
\todo{cite sparse gp papers}
Instead of collapsing the inducing variables like \cite{titsiasVariational2009}, they can be treated variationally
$p(\mathbf{u} \mid \mathbf{y}) \approx q(\mathbf{u}) = \mathcal{N}\left( \mathbf{u} \mid \mathbf{m}, \mathbf{V} \right)$, where $\mathbf{m}$ and $\mathbf{V}$ are variational parameters
which need to be optimised \parencite{hensmanGaussian2013}.
The sparse variational GP (SVGP) predictive posterior is then given by,
\begin{align}
\label{eq-dual-svgp-predictive-posterior}
  p(f(\mathbf{x}_{*}) \mid \mathbf{y})
&\approx \mathcal{N} \left( f(\mathbf{x}_{*}) \mid \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{m}^{*},
  k_{**} - \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
  % \mathbf{k}_{*\inducingInput} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\inducingInput}^{T}
  + \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}}  \mathbf{V}^{*}  \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
  \right)
\coloneqq q_{\inducingVariable}(f(\mathbf{x}_{*}))
\end{align}

\textbf{Deep learning}
Given the data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
the goal of (supervised) deep learning, is to train the weights $\transitionParams \in \R^{P}$ of an $L\text{-layer}$ NN
$f : \inputDomain \rightarrow \outputDomain$ to minimize the (regularized) empirical risk,
\begin{align} \label{eq-empirical-risk}
  \transitionParams^{*} = \arg \min_{\transitionParams \in \R^{D}} \mathcal{L}(\dataset;\transitionParams) = \arg \min_{\transitionParams \in \R^{D}} \left(
  R(\transitionParams) + \sum_{n=0}^{N-1} l(f(\mathbf{x}_{n} ; \transitionParams), \mathbf{y}_{n}) \right).
\end{align}
In practice, it is common to use the mean squared error (MSE) loss
$l(f(\mathbf{x}_{n} ; \transitionParams),\mathbf{y}_{n}) = \|f(\mathbf{x}_{n} ; \transitionParams) - \mathbf{y}_{n} \|^{2}_{2}$
and to use the weight decay regularizer $R(\transitionParams)=\frac{1}{2}\gamma^{-2}\|\transitionParams\|^{2}_{2}$.
However, the practioner is free to choose any loss and regularizer. \todo{I think?}
% \textbf{Bayesian neural networks}
% \textbf{Weight space to function space}
From a Bayesian perspective, we can interpret the terms in \cref{eq-empirical-risk} as the log-prior and the i.i.d. log likelihood, i.e.,
\begin{align} \label{eq-log-prior}
  R(\transitionParams) &= \underbrace{\log p(\transitionParams)}_{\text{log prior}} = \log \mathcal{N}(\transitionParams \mid 0, \gamma^{2} \mathbf{I}) \\
  l(f(\mathbf{x}_{n} ; \transitionParams), \mathbf{y}_{n}) &= \underbrace{\log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \transitionParams))}_{\text{log likelihood}}
  = \log \mathcal{N} \left( \mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \transitionParams), \mathbf{I} \right) \label{eq-log-likelihood}
\end{align}

\textbf{NN to GP}
Given this interpretation, we can represent the weight space prior from \cref{eq-log-prior}, in
function space, by linearising the BNN around $\transitionParams^{*}$ and interpretting it as a GP.
The GP prior is then given by,
\begin{align} \label{eq-laplace-approx-function-space}
  % \transitionFn_{\transitionParams_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \qquad
  f(\cdot ;\transitionParams) \sim \mathcal{N} \left( \mu(\cdot), k(\cdot, \cdot') \right) \quad
  % \mu_{\transitionParams_{i}^{*}}(\cdot)
  \mu(\cdot)
  = 0 \quad
  % = f(\cdot ;\transitionParams^{*}) \quad
  % K_{\transitionParams_{i}^{*}}(\cdot, \cdot')
  k(\cdot, \cdot')
  = \frac{1}{\gamma^{2}} \mathbf{J}(\cdot) \mathbf{J}(\cdot')^{T},
\end{align}
where the kernel is the neural tangent kernel (NTK) \parencite{immerImprovingPredictionsBayesian2021},
\todo{what mean function shoudl this use???}
\todo{NTK times some factor??}
with Jacobian given by $\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \transitionParams)}{\transitionParams}_{\transitionParams=\transitionParams^{*}}$.
% The kernel in \cref{eq-laplace-approx-function-space} is the neural tangent kernel (NTK)
% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\transitionParams^{*}}(\mathbf{x}) J_{\transitionParams^{*}}(\mathbf{x}')^{T}$
% \parencite{immerImprovingPredictionsBayesian2021}
% to formulate the GP posterior $p(f(\mathbf{X} ;\transitionParams_{0:i}) \mid \dataset_{0:i})$.
Given this GP prior, we can use \cref{eq-gp-predictive-posterior} to obtain our GP posterior by conditioning on the data.
% Given our GP prior, we can use the properties of multivariate normals to obtain our GP posterior by conditioning on the data.
% where $\mathbf{A} = \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}}$
In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
Intuitively, we can view the optimisation in \cref{eq-empirical-risk} as learning our kernel.
As a result, our NTK may be highly non stationary as it is dependent on the NN architecture, for example, the activation functions.
It is worth noting that the NTK linearises the network around the optimised parameters $\transitionParams^{*}$,
so the function space prior (and thus posterior) is only a locally linear approximation.

We now have a method to obtain a GP posterior from a trained DNN.
% In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior obtained from the Laplace approximation.
In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior from a BNN.
However, in practice, the GP posterior is not very useful as it requires inverting an $N\times N$ matrix which has complexity $\mathcal{O}(N^{3})$.
The SVGP in \cref{eq-dual-svgp-predictive-posterior} offers a solution to this problem but it is not immediately clear how to set $\mathbf{m}$ and $\mathbf{V}$.
In the next section, we show how we can directly obtain an SVGP posterior (i.e. set $\mathbf{m}$ and $\mathbf{V}$) directly from both
1) a trained NN and 2) a BNN weight-space posterior.
% $\mathbf{m}$ and $\mathbf{V}$
% However, it is not obvious how we can use a SVGP to set $\mathbf{m}$ and $\mathbf{V}$

% In contrast, to previous work, this approach did not require us Laplace approximation. we will not restrict our
% It is worth noting that the NTK linearises the network around the optimised parameters $\transitionParams^{*}$,
% so the function space prior (and thus posterior) is only a locally linear approximation.
% In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
% It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.

\section{Method}
In the next section we show how we can obtain a SVGP directly from 1) a trained NN and 2) a BNN posterior.

@@

\section{Experiments}

% \begin{figure}
%   \centering
%   \includegraphics[width=0.5\textwidth, angle=270]{figs/weight-space-to-functio-space.pdf}
%   \caption{}
% \end{figure}

% \begin{figure}
%   \centering
%   \includegraphics[width=0.5\textwidth, trim=0 100 0 10]{figs/cartpole-training-curves.pdf}
%   \caption{}
% \end{figure}

% \begin{table}
%   \caption{Negative test log likelihood (lower is better) on UCI classification tasks (2 hidden layers, 50 tanh). Our SVGP predictive outperforms the GLM predictive. }
% \end{table}

\begin{itemize}
  \item Show prediction performance in classification: UCI classification results, compare to BNN predictive paper
  \item Fast adapatation in model-based RL: results for cartpole
  \item Is linearising NN mean and using fast updates during episode better than keeping non-linearised mean and not updating?
  \item Possible ablations
  \begin{itemize}
    \item How does number of inducing points affect performance?
  \end{itemize}
  \item How good is the assumption that we can linearise BNN to get NTK?
\end{itemize}

Environments
\begin{itemize}
  \item Compare updated posterior with non updated posterior
  \item Need to show update is fast enough for practical use?
  \begin{itemize}
    \item How frequently can we do the posterior update? Every time step or every $K$ steps?
    \item Update depends on number of inducing points?
    \item What experiments can we show for this? Wall clock time vs planning horizon with different numbers of inducing points?
  \end{itemize}
  \item Is linearising NN mean and using fast updates during episode better than keeping non-linearised mean and not updating?
  \item How does number of inducing points affect performance?
  \begin{itemize}
    \item More inducing points means better approximation but larger computational complexity.
  \end{itemize}
  \item How good is the assumption that we can linearise BNN to get NTK?
  \begin{itemize}
    \item Does model's performance get worse during an episode because linearisation becomes more wrong?
    \item SVGP does't have this issue so compare to SVGP in cartpole?
  \end{itemize}
  \item What length planning horizon to use?
  \begin{itemize}
    \item Too small (e.g. $\Horizon=0$) would mean no exploration?
    \item Can $\Horizon$ be too large?
  \end{itemize}
  \begin{itemize}
  \item Compare for different strategies of making decisions under dynamic model's uncertainty:
    \begin{itemize}
      \item \textbf{Greedy exploitation} \(\pi_{\text{greedy}}\)
      \item \textbf{Hallucinated-UCRL} \(\pi_{\text{HUCRL}}\)
      \item \textbf{Thompson sampling} \(\pi_{\text{TS}}\)
    \end{itemize}
  \end{itemize}
  \item Compare impact of stationary vs non-stationary priors
  \begin{itemize}
    \item First do this with GP
    \item Then try to do with Laplace BNN
  \end{itemize}
  \item Compare impact of function vs weight space
\end{itemize}

@@

\textbf{Laplace approximation}
The Laplace approximation \todo{add citation of original paper} constructs a Gaussian approximation of the weight-space posterior $p(\transitionParams \mid \dataset)$
by using a second-order Taylor expansion of $\mathcal{L}$ around $\transitionParams^{*}$.
The posterior approximation is given by,
\begin{align} \label{eq-laplace-approx-weight-space}
  p(\transitionParams \mid \dataset) \approx \mathcal{N} \left( \transitionParams \mid \transitionParams^{*} , \bm\Sigma_{\transitionParams^{*}} \right)
  \quad \text{with} \quad \bm\Sigma_{\transitionParams} =
 - \nabla_{\transitionParams \transitionParams}^{2} \mathcal{L} ( \dataset ; \transitionParams)|_{\transitionParams=\transitionParams^{*}}
\end{align}
That is, it sets the posterior precision to the Hessian of the loss at the optimal parameters $\transitionParams^{*}$.
It is worth noting that computing the Hessian of the loss can be computationally intractable for large networks.
The prior terms are usually trivial, so we focus on the likelihood here.
The Jacobian and Hessian of the log likelihood can be expressed per data point,
\begin{align} \label{eq-jac}
  \nabla_{\transitionParams} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \transitionParams)) &= \mathbf{J}(\mathbf{x})^{T} \mathbf{r}(\mathbf{y} ; \mathbf{f}) \\
  \nabla^{2}_{\transitionParams\transitionParams} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \transitionParams)) &= \mathbf{H}(\mathbf{x})^{T}
  \mathbf{r}(\mathbf{y};\mathbf{f}) - \mathbf{J}(\mathbf{x})^{T} \bm\Lambda(\mathbf{y};\mathbf{f}) \mathbf{J}(\mathbf{x}),
\label{eq-hess}
\end{align}
through the Jacobian $\mathbf{J} \in \R^{C \times P}$ and Hessian $\mathbf{H} \in \R^{C \times P \times P}$ of the feature extractor $\mathbf{f}(\mathbf{x}; \bm\transitionParams)$,
\begin{align} \label{eq-jac}
[\mathbf{J}(\cdot)]_{ci} = \odv{f_{c}(\cdot ; \transitionParams)}{\transitionParams_{i}}_{\transitionParams=\transitionParams^{*}} \qquad
[\mathbf{H}(\cdot)]_{cij} = \odv{f_{c}(\cdot ; \transitionParams)}{\transitionParams_{i}\transitionParams_{j}}_{\transitionParams=\transitionParams^{*}}
\end{align}
where
$\mathbf{r}(\mathbf{y}; \mathbf{f}) = \nabla_{\mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be interpreted as a residual and
$\bm\Lambda(\mathbf{y} ; \mathbf{f}) = \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$
as per-input noise.
Many approximations exist and can be used alongsied our method.
We refer the reader to \cite{daxbergerLaplace2021} for more details.
See \cref{sec-laplace-approximation} for further details on the Laplace approximation.
